---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trydustevents

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of trydustevents from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("pratikunterwegs/trydustevents")
```

## Get started

The model has defaults that show event functionality; the NPI event is active from day 30 -- day 60.

```{r}
library(trydustevents)

data = run_model()

plot(data$I)
```

## Modifying ODEs

This is a multi-step process involving a `dust2` object:

1. Modify the ODE system in `inst/dust/model.cpp` --- this is a member function of the `sirode` class. This class name can be changed, but remember to change it within `R/model.R` as well as it must be consistent throughout the package;

2. Run `dust2::dust_package(".")` from within the package directory;

3. Run `devtools::load_all()` as usual with any other package.
